Paper Title

### 2022-11-04 paper/include/structure.tex
remove necessity for make

\begin{figure*}
		\centering
	\begin{subfigure}[c]{0.45\textwidth}
				\centering
		\includegraphics[width=.4\textwidth]{pics/example}
		\subcaption{An external figure.}
		\label{fig:external_pdf}	
	\end{subfigure}
	\begin{subfigure}[c]{0.45\textwidth}
		\includegraphics[width=\textwidth]{figures/example}
		\subcaption{An external figure which was built before included.}
		\label{fig:external_tex}
	\end{subfigure}
	\caption{This Figure has two subfigures and spans both columns.}
\end{figure*}

@@

	\item[\texttt{/figures}:] If you do not want to build all your figures
	every time you compile your paper it is helpful to build them
	separately. All \texttt{.tex} and \texttt{.tikz} files within this directory
	are built automatically by the Makefile. Since these figures are built
	independently of the main document they have to be of type
	\texttt{standalone}. Make sure that you put no \texttt{.tex} or
	\texttt{.tikz} inside this directory which cannot be compiled
	independently.
	Figure~\ref{fig:external_tex} is an example for this. Notice that this
	PDF is only built if the figures source file has changed.

	\item[\texttt{/data}:] If you have larger amounts of data which you
	want to put into your paper, for example in form of a table or a plot
	you can import the data directly from another file.
	Figure~\ref{fig:external_tex} reads the red sample points from a CSV
	file located in this directory.
\end{itemize}

>>>>

\begin{figure*}
		\centering
	\begin{subfigure}[c]{0.45\textwidth}
				\centering
		\includegraphics[width=.4\textwidth]{pics/example}
		\subcaption{An external figure.}
		\label{fig:external_pdf}	
	\end{subfigure}
\end{figure*}

@@

	\item[\texttt{/data}:] If you have larger amounts of data which you
	want to put into your paper, for example in form of a table or a plot
	you can import the data directly from another file.
\end{itemize}
